### 2016-09-26 assumptions.tex
Discuss Rete algorithm and new assumptions in the logic section
This should help our rebuttal point for keeping the supplement logic
subsection in the supplement.

SymPy performs logical inference through its assumptions system. The
assumptions system allows users to specify that symbols have certain common
mathematical properties, such as being positive, imaginary, or integral. SymPy
is careful to never perform simplifications on an expression unless the
assumptions allow them. For instance, the identity $\sqrt{t^2} = t$ holds if
$t$ is nonnegative ($t\ge 0$). However, for general complex $t$, no
such identity holds.

@@

Basic implications between the facts are used to deduce assumptions. For
instance, the assumptions system knows that being an integer implies being
rational.
\begin{verbatim}
>>> i = Symbol('i', integer=True)
>>> i.is_rational
True
\end{verbatim}
Furthermore, expressions compute the assumptions on themselves
based on the assumptions of their arguments. For instance, if \texttt{x} and
\texttt{y} are both created with \texttt{positive=True}, then
\texttt{(x + y).is\_positive} will be \texttt{True} whereas
\texttt{(x - y).is\_positive} will be \texttt{None}.

>>>>

The assumptions system allows users to specify that symbols have certain
common mathematical properties, such as being positive, imaginary, or
integral. SymPy is careful to never perform simplifications on an expression
unless the assumptions allow them. For instance, the identity $\sqrt{t^2} = t$
holds if $t$ is nonnegative ($t\ge 0$). However, for general complex $t$, no
such identity holds.

@@

Basic implications between the facts are used to deduce assumptions.
Deductions are made using the Rete
algorithm~\cite{doorenbos1995production}.\footnote{For historical reasons,
  this algorithm is distinct from the \texttt{sympy.logic} submodule, which is
  discussed in the supplementary material. SymPy has an experimental
  assumptions system which stores facts separate from objects, and uses
  \texttt{sympy.logic} and a SAT solver for deduction. We will not discuss
  this system here.} For instance, the assumptions system knows that being an
integer implies being rational.
\begin{verbatim}
>>> i = Symbol('i', integer=True)
>>> i.is_rational
True
\end{verbatim}
Furthermore, expressions compute the assumptions on themselves
based on the assumptions of their arguments. For instance, if \texttt{x} and
\texttt{y} are both created with \texttt{positive=True}, then
\texttt{(x + y).is\_positive} will be \texttt{True} whereas
\texttt{(x - y).is\_positive} will be \texttt{None}.
